
\experience{%
  \job{Yume Arcade}{November 2023 -- Current}{Founder \& CTO}%
  {Java -- Spring, NextJS, Postgres, Network Architecture}{%
  \item Founded and led all technical development for a physical arcade business, scaling it to \$XXK/month in revenue as the sole engineer owning software, hardware, firmware, and network infrastructure end-to-end.
  \item Designed and manufactured custom PCB hardware with ESP32 (Arduino/C++) firmware to power a proprietary arcade credit system, enabling deep hardware-software integration and full control over the payment and session lifecycle.
  \item Built bespoke backend services to manage credits, user actions, and device state synchronization across machines, maintaining zero production downtime since launch.
  \item Designed and deployed an on-premises server architecture enabling fully offline operation, eliminating dependency on internet connectivity and ensuring sub-100ms payment latency at all times.
  \item Engineered, manufactured, and deployed self-service customer kiosks integrating NFC chips, multi-card dispensers, and Square payment APIs — cutting required clerk headcount by 50\% and redirecting staff to higher-value customer interactions.
  \item Built a digital queue management system and customer-facing app that optimized peak-hour throughput, driving an estimated 10\% increase in revenue per hour.
  }%
  \job{ShareSFR}{November 2024 -- Current}{Senior Software Developer}%
  {Python, Langchain -- OpenAI, Postgres, AWS}{%
  \item Sole engineer responsible for designing and delivering an AI-driven document ingestion platform capable of processing 3,000 unstructured legal and financial documents per day into normalized, queryable database models.
  \item Optimized the full pipeline to operate within AWS micro-instance constraints, reducing per-document processing cost by 75\% while preserving throughput and reliability at scale.
  \item Architected multi-step LLM pipelines using OpenAI models to automate document classification, entity extraction, and date parsing - transforming raw, unstructured input into serialized, versioned records with no manual intervention.
  \item Designed and implemented a confidence scoring and thresholding system to surface uncertain AI outputs for human review, improving downstream data quality and reducing silent errors in production.
  \item Eliminated manual document tagging bottlenecks, enabling the business to onboard new data sources faster and materially increasing the volume of documents processed per analyst per day.
  \item Owned all architecture decisions, data modeling, and operational tradeoffs for a production AI system end-to-end under significant infrastructure and model performance constraints.
  }%
  \job{Loblaw Digital}{November 2019 -- November 2024}{Software Developer}%
  {Java -- Spring, Elixir -- Phoenix, GCP, PostgreSQL}{%
  \item One of 4 engineers trusted with ownership of 2 critical, revenue-impacting services within a 100-person engineering org at Canada's largest retailer.
  \item Designed and delivered a real-time stock visibility feature for the cart service, integrating live inventory feeds with data-science-predicted stock levels to reduce product substitutions and improve the end-to-end customer shopping experience.
  \item Overhauled logging and alerting infrastructure across core service components, cutting false positive alerts by ~50\% while increasing signal fidelity - giving the on-call team clearer, more actionable insight into real system errors.
  \item Introduced CI/CD performance testing baselines that established continuous visibility into service health, enabling the team to catch regressions before production and maintain P99 SLA compliance across all deployments.
  \item Reduced P95 API latency by 15\% and improved performance for large cart operations by 25\% through targeted profiling and refactoring of critical service functions.
  \item Designed and built new microservice components with a focus on performance, maintainability, and long-term code quality across a high-traffic production system.
  }%
}
